Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Humorous swedish abstract placeholder

\begin{otherlanguage}{swedish}
  \begin{abstract}
    Träutensilierna i ett tryckeri äro ingalunda en oviktig faktor,
    för trevnadens, ordningens och ekonomiens upprätthållande, och
    dock är det icke sällan som sorgliga erfarenheter göras på grund
    af det oförstånd med hvilket kaster, formbräden och regaler
    tillverkas och försäljas Kaster som äro dåligt hopkomna och af
    otillräckligt.
  \end{abstract}
\end{otherlanguage}

>>>>

\begin{otherlanguage}{swedish}
\begin{abstract}
Haha, He-Man! There is no possible way that you feeble-brained barbarian and your furball mount can foil my plan this time. With the ancient power at my command I shall doom this kingdom to crumble in meager ashes and.. Oh shit, he has run off with the crystal skull hasn't he? Damn you He-Man!!!

\end{abstract}
\end{otherlanguage}
